### 2023-06-06 manuscript.Rmd
Update manuscript.Rmd
Co-authored-by: Aaron Peikert <aaron.peikert@posteo.de>

At present, whether a piece of software is open source is not evaluated at the pre-screening stage.
However, an open license is central for assessing both rigor and (potential) impact, and should be part of the phase I assessment.
Above, we already discussed the different ways research software can have an impact --- not only by direct usage, but also by reusing software in other packages.
Open-source software makes broader impact more likely and is a prerequisite for full transparency and reproducibility [@peikert2021reproducible].
In addition, many aspects of rigor are impossible to evaluate for closed-source software --- for example, whether it is well-tested or bugs have been fixed.
Giving more weight to open licenses aligns well with the original article's emphasis on open science.
Therefore, we propose to penalize software if it does not adhere to an open-source license (those approved in a review process by the Open Source Initiative (https://opensource.org/licenses), for example, by allowing them only half of the total achievable points.

>>>>

At present, whether a piece of software is open source is not evaluated at the pre-screening stage.
However, an open license is central for assessing both rigor and (potential) impact, and should be part of the phase I assessment.
Above, we already discussed the different ways research software can have an impact --- not only by direct usage, but also by reusing software in other packages.
Open-source software makes broader impact more likely and is a prerequisite for full transparency and reproducibility [@peikert2021reproducible].
In addition, many aspects of rigor are impossible to evaluate for closed-source software --- for example, whether it is well-tested or bugs have been fixed.
Giving more weight to open licenses aligns well with the original article's emphasis on open science.
Therefore, we propose to penalize software if it does not adhere to an open-source license (those approved in a review process by the [Open Source Initiative](https://opensource.org/licenses)), for example, by allowing them only half of the total achievable points.
